---
title: "Epidemic Simulation Report"
output: pdf_document
params:
  report: NULL
always_allow_html: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
report <- params$report
library(ggplot2)
library(knitr)
```

**Disease:** `r report$metadata$disease`  **Model:** `r report$metadata$model`  **Generated:** `r report$metadata$generated_at`

---

## Simulation Parameters

```{r}
if (!is.null(report$sim_data)) {
  param_df <- data.frame(
    Parameter = c("Transmission rate (beta)", "Recovery rate (gamma)", "Population",
                   "Vaccination coverage", "Initial infected", "Basic reproduction number (R0)"),
    Value = c(
      report$parameters$transmission_rate_beta,
      report$parameters$recovery_rate_gamma,
      format(report$parameters$population, big.mark = ","),
      paste0(report$parameters$vaccination_coverage_pct, "%"),
      report$parameters$initial_infected,
      report$parameters$basic_reproduction_number_R0
    )
  )
  kable(param_df)
} else {
  cat(report$parameters$note)
}
```

## Epidemic Curve

```{r, fig.width=6.4, fig.height=3.2}
if (!is.null(report$sim_data)) {
  df <- report$sim_data
  has_E <- "E" %in% names(df)
  plot_df <- data.frame(day = df$day, Susceptible = df$S, Infected = df$I, Recovered = df$R)
  plot_long <- reshape(plot_df, direction = "long", varying = list(2:4),
                        v.names = "value", timevar = "compartment",
                        times = c("Susceptible", "Infected", "Recovered"))
  ggplot(plot_long, aes(x = day, y = value, color = compartment)) +
    geom_line(linewidth = 1) +
    scale_color_manual(values = c(Susceptible = "#B7791F", Infected = "#3182CE", Recovered = "#2E7D4E")) +
    labs(x = "Day", y = "People", color = NULL,
         title = paste("Simulated Epidemic Curve --", report$metadata$disease, paste0("(", report$metadata$model, ")"))) +
    theme_minimal(base_size = 10) +
    theme(legend.position = "top")
} else {
  cat("No simulated curve is generated for", report$metadata$disease, "-- see the note below.")
}
```

## Key Results

```{r}
result_df <- data.frame(
  Metric = names(report$results),
  Value = vapply(report$results, function(v) paste(v, collapse = "; "), character(1))
)
kable(result_df)
```

## Real-World Comparison

`r report$real_world_reference$note`

Source type: **`r report$real_world_reference$source`**  ·  Fetched/generated at: `r report$real_world_reference$fetched_at`

---

> **Note:** This report contains SIMULATED results generated from user-set parameters using a compartmental
> epidemic model (SIR/SEIR/SIRS). It is a scenario projection, not a verified real-world forecast.
> Real-world reference figures are cited from their original source and are kept separate from the
> simulation outputs above.
